Title

### 2023-08-14 manu-draft.qmd
initial workflow for fim data import
adding documentation about thresholds

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "Title"
# bibliography: refs.bib
# csl: limnology-and-oceanography.csl
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true

@@

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "Title"
bibliography: refs.bib
# csl: limnology-and-oceanography.csl
author: 
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true

@@

Salinity tolerance: Ruppia \> Halodule\> Thalassia \> Syringodium

Halodule:

-   Temp: 20-30 (range, @lewis1985)

-   Salinity: grows well in most salinity ranges [@lirman2003], like Syringodium but more tolerant [@lewis1985], 10-35 (range) or \< 10 (S. Scolaro)

Thalassia:

-   Temp: 20-30 (range, @lewis1985, @zieman75), 30-31 (upper, from SS)

-   Salinity: 25 (lower, @lewis1985); 30, lowest at 5 (lower, @lirman2003), 33-38 (range, @phillips1960); 24-35 (range, @zieman1975 citing @phillips1960)

Syringodium:

-   Temp: 20-30 (range, @lewis1985), 29 (upper from SS)

-   Salinity: 20 (lower, @lewis1985), 25 (lower, @lirman),

@lewis1985 review of seagrass in Tampa Bay. @lirman2003 conducted exposure experiments to evaluate seagrass growth in response to a range of salinity conditions. @mcmillan1967 discusses growth of halodule, syringodium, thalassia, and ruppia in response to salinity increases (up to 75 psu), no info on lower limit. Cites @phillips1960 for a salinity range of Thalassia in Florida of 33 - 38 psu. @zieman1975 discusses seasonal variation of thalassia relative to temp and salinity

-   Get FIM, Pinellas, Manatee data
